\vspace{-2cm} The effects of transitions of power on the contents of municipal government websites

### 2017-07-17 paper/manuscript.tex
code to run LDA with mallet + results figure (word-topic probabilities) added to manuscript. I only added the one for the wget website content, the wayback machine ones look strange because they contain words that are too long (and also do not exist)
added the mallet and hunspell stuff
added comparison of topic prevalence in democratic and republican cities

\begin{figure}[!ht]
	\centering
	%\caption{Population coverage}
	\includegraphics[width=\linewidth]{figures/wtpIndy.pdf}
\end{figure}

% latex table generated in R 3.3.2 by xtable 1.8-2 package
% Fri Mar 24 12:52:43 2017
\begin{table}[ht]
\centering
\begin{tabular}{lrrrr}
  \hline
File type & oct15 & jan16 & feb16 & mar16 \\ 
  \hline
.pdf & 179 & 183 & 111 & 197 \\ 
  .aspx &  99 & 112 & 116 &  76 \\ 
  .jpg &  22 &  24 &  17 &  12 \\ 
  .gif &   3 &   5 &   1 &   5 \\ 
  .JPG &   3 &   2 &   1 &   5 \\ 
  .png &   3 &   7 &   2 &   1 \\ 
  .asmx &   2 &   1 &   1 &   5 \\ 
  .PDF &   1 &   1 &   1 &   2 \\ 
   \hline
\end{tabular}
\caption{File types of Indy.gov at different points in time} 
\end{table}

>>>>

\begin{figure}[!ht]
	\centering
	%\caption{Population coverage}
	\includegraphics[width=\linewidth]{figures/wtp_current.pdf}
\end{figure}

\begin{figure}[!ht]
	\centering
	%\caption{Population coverage}
	\includegraphics[width=\linewidth]{figures/wtp_current_dem_rep.pdf}
\end{figure}

%\begin{figure}[!ht]
%	\centering
	%\caption{Population coverage}
%	\includegraphics[width=\linewidth]{figures/wtp_before.pdf}
%\end{figure}

%\begin{figure}[!ht]
%	\centering
	%\caption{Population coverage}
%	\includegraphics[width=\linewidth]{figures/wtp_after.pdf}
%\end{figure}

\begin{figure}[!ht]
	\centering
	%\caption{Population coverage}
	\includegraphics[width=\linewidth]{figures/wtp_current_dem_rep_order.pdf}
\end{figure}
